---
title: "Untitled"
author: "Jonathan Bourne"
date: "7 June 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r}
packages <- c("tidyverse", "igraph","readr","readxl", "broom", "zoo", "stringr","foreach", "doMC",  "xtable", "geomnet", "ggnetwork", "rlang", "animation", "ggridges", "poweRlaw", "Rtsne", "caret", "ranger", "xtable", "broom", "modelr", "yardstick", "rgeos", "sp", "rgdal")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)


sapply(packages, library, character.only = TRUE)


lapply(packages, library, character.only = TRUE)
library(PowerGridNetworking)

datafolder <- "/home/jonno/ModellingInternationalNetworks/entsoe_extract"
WorldShapeFile <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder/WorldBoarders"

setwd(datafolder)
buses <- read_csv("buses.csv", quote="'")
links <- read_csv("links.csv",  quote="'")
generators <- read_csv("generators.csv",  quote="'")
transformers <- read_csv("transformers.csv",  quote="'")

```

#Tag Cleaning

This chunk creates the function required to seperate the tags on the network.
```{r}

AddTags <- function(df){
  
  test1 <- df %>% 
  mutate(tags =  ifelse(is.na(tags), "Empty\"=>\"TRUE", tags)) %>% .$tags %>% 
  str_split(., "," )  

test2 <- 1:length(test1) %>% 
  map_df(., ~{
         HasSplit <- grepl("=>", test1[[.x]])
        df <- str_split(test1[[.x]][HasSplit], "=>", simplify = T ) %>%
        gsub("\"", "",.) %>% as_tibble() %>%
          mutate(row= .x,
                 V1 = trimws(V1)) 
          }
      )   %>% 
          spread(key = V1, value = V2)

df <- bind_cols(df, test2)
  
}

```

#Clean Country

```{r}

buses2 <- AddTags(buses) 

buses2 <- buses2$geometry %>% gsub("POINT\\(", "", .) %>% 
  gsub("\\)", "",.) %>%
  str_split_fixed(., " ", 2) %>% as_tibble() %>%
  mutate_all(as.numeric) %>%
  set_names(c("x", "y")) %>% bind_cols(buses2, .)

generators2 <-AddTags(generators)

links2 <- AddTags(links) %>%
  select(src_bus_id, dst_bus_id, everything())


#links2 %>%
 # filter(!is.na(tags)) %>%
#ggplot(.,aes(x= as.numeric(shape_leng), group = country_1 )) + geom_density() 

```


#Create Entsoe basegraph
```{r}
gbaseEnt <- graph_from_data_frame(links2, directed = FALSE, vertices = buses2)
```


#Subsets graph by country
```{r}

SubsetCountry<- function(graph, country_name, vertex_id = "name", country_id = "country"){

  NodeCountry<- tibble(VertexName = get.vertex.attribute(gbaseEnt, vertex_id), 
                     country = get.vertex.attribute(gbaseEnt, country_id)) %>%
  filter(country != country_name | is.na(country))

  Out <- delete_vertices(gbaseEnt, NodeCountry$VertexName)
  
  return(Out)

}

```


TAG all nodes if they are NA and inside a countries borders
```{r}
setwd(WorldShapeFile)
borders <- readOGR("TM_WORLD_BORDERS-0.3.shp")


#Pre-Loop
buses2 <- buses2 %>%
  mutate(BorderCount = NA)

Countries<- unique(buses2$country)

for(ISO2 in Countries[!is.na(Countries)]){

  #In loop
  borders2<- borders[borders@data$ISO2==ISO2,]
  
  Countrydf <-  data.frame(bus_id = buses2$bus_id, Latitude = buses2$x, Longitude = buses2$y, buses2$name_eng)
  
  coordinates(Countrydf) <- ~ Latitude + Longitude
  
  # Set the projection of the SpatialPointsDataFrame using the projection of the shapefile
  proj4string(Countrydf) <- proj4string(borders2)
  
  Out <-Countrydf[borders2,] %>% as.data.frame %>%
    mutate(BorderCount = ISO2) %>%
    select(bus_id, BorderCount)
  
  buses2 <- buses2 %>%
    mutate(BorderCount = ifelse(bus_id %in% Out$bus_id, ISO2, BorderCount))
  
}

buses2 <- buses2 %>%
  mutate(BorderCount = ifelse(is.na(country), BorderCount, country))


gbaseEnt <- graph_from_data_frame(links2, directed = FALSE, vertices = buses2)

```

#Tag 2

Tag all nodes if they are in the network of some other node that has a country
```{r}
VertexCountry <-  tibble(name = get.vertex.attribute(gbaseEnt, "name"), 
                 country = get.vertex.attribute(gbaseEnt, "BorderCount")) %>%
  mutate(name = as.integer(name))

 
#insert the country code of each node into the links data frame
LinksPLus <- links2 %>% left_join(., VertexCountry, by = c("src_bus_id" = "name")) %>%
  rename(countryRep1 = country) %>%
  left_join(., VertexCountry, by = c("dst_bus_id" = "name")) %>%
  rename(countryRep2 = country)

#find that it is different to the original
table(is.na(LinksPLus$country_1), is.na(LinksPLus$countryRep1))
table(is.na(LinksPLus$country_2), is.na(LinksPLus$countryRep2))
table(is.na(LinksPLus$countryRep1), is.na(LinksPLus$countryRep2))

LinksPLus2 <- LinksPLus

for(i in 1:5){
  
  Missing1 <-sum(is.na(LinksPLus2$countryRep1))
  Missing2 <-sum(is.na(LinksPLus2$countryRep2))
  
  LinksPLus2 <- LinksPLus2 %>%
    mutate(countryRep2 = ifelse(is.na(countryRep2), countryRep1, countryRep2),
           countryRep2 = ifelse(is.na(countryRep2), country_2, countryRep2))
 
  New2 <- sum(is.na(LinksPLus2$countryRep2))
  print(paste("Missing2 removed", Missing2 - New2) )
  LinksPLus2 <- LinksPLus2 %>%
    mutate(countryRep1 = ifelse(is.na(countryRep1), countryRep2, countryRep1),
            countryRep1 = ifelse(is.na(countryRep1), country_1, countryRep1))  
  
    New3 <- sum(is.na(LinksPLus2$countryRep2))
  print(paste("Missing1 removed", Missing1 - New3) )

  }

table(is.na(LinksPLus2$country_1), is.na(LinksPLus2$countryRep1))
table(is.na(LinksPLus2$country_2), is.na(LinksPLus2$countryRep2))
table(is.na(LinksPLus2$countryRep1), is.na(LinksPLus2$countryRep2))

#only two nodes remaining untagged both are in GB
test <- LinksPLus2 %>%
  filter(country_1 == "GB")


  VertexCountry <- bind_rows(LinksPLus2 %>% 
                               select(src_bus_id, countryRep1) %>% 
                               rename(bus_id = src_bus_id, country = countryRep1), 
                             LinksPLus2 %>% 
                               select(dst_bus_id, countryRep2)%>% 
                               rename(bus_id = dst_bus_id, country = countryRep2)) %>%
    group_by(bus_id) %>%
    summarise(country = first(country)) %>% ungroup %>%
    mutate(country = ifelse(is.na(country), "GB", country))
    

buses2 <- buses2 %>% select(-country,-BorderCount) %>%
  left_join(VertexCountry)
rm(VertexCountry); rm(LinksPLus); rm(LinksPLus2)

BusCountry <- buses2 %>% select(bus_id, country)

links2 <- links2 %>%
  select(-country_1, -country_2) %>%
  left_join(., BusCountry, by= c("src_bus_id"= "bus_id")) %>%
  rename(country_1 = country) %>%
  left_join(., BusCountry, by= c("dst_bus_id"= "bus_id")) %>%
  rename(country_2 = country)

```


#Clean graph with all nodes having a country
```{r}
gbaseEnt <- graph_from_data_frame(links2, directed = FALSE, vertices = buses2)
```


Filter By country


#Plot Country grid
```{r}

SubsetCountry(gbaseEnt, "GB") %>%
  simplify(., remove.multiple = T, remove.loops = T) %>% 
  plot(.,vertex.size=.8, edge.arrow.size=.4, vertex.label = NA, 
       layout=as.matrix(tibble(x = get.vertex.attribute(., "x"), y = get.vertex.attribute(., "y"))) )

SubsetCountry(gbaseEnt, "NO") %>%
  simplify(., remove.multiple = T, remove.loops = T) %>% 
  plot(.,vertex.size=.8, edge.arrow.size=.4, vertex.label = NA)



GBnet <- SubsetCountry(gbaseEnt, "GB")
GBnet %>% NetworkStats

components(GBnet)

gbaseEnt %>% components()
gbaseEnt %>% NetworkStats

test <- fit_power_law(degree(gbaseEnt))

test <- fit_power_law(degree(GBnet))


```

```{r}

CountriesOI <-  c("NO", "GB", "ES", "FR", "DE", "IT", "PL")

links2 %>%
  filter(country_1 ==  country_2) %>%
  filter(country_1 %in% CountriesOI) %>%
ggplot(.,aes(x= as.numeric(shape_leng), colour = country_1 )) + geom_density()

test <- CountriesOI %>% map_df(~{
  SubsetCountry(gbaseEnt, .x) %>% NetworkStats %>%
    set_names(c("Metric", .x))
    #mutate(Country = .x)
}) %>%
  spread(Country, value) 

NetworkCompare <- CountriesOI %>% map(~{
  SubsetCountry(gbaseEnt, .x) %>% NetworkStats %>%
    mutate(value = round(value, 2)) %>%
    set_names(c("Metric", .x))
    #mutate(Country = .x)
}) %>% reduce(., left_join)

```


